Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-23 analysis/paper/paper.Rmd
Clarify table 1's caption

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>% 
  rename(Journal = journal,
         `5 Year IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  autofit() %>%
  set_caption(
    "Journal titles selected for inclusion, their respective five year impact factors as of 2022 and the number (n) of articles from each journal that were evaluated."
  )
```

>>>>

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>% 
  rename(Journal = journal,
         `5 Year IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  autofit() %>%
  set_caption(
    "Journal titles selected for inclusion, their respective five year impact factors as of 2022 (5 Year IF) and the number (n) of articles from each journal that were evaluated."
  )
```
